% \documentclass{letter}
\documentclass[10pt,stdletternofrom,letterpaper,dateno,sigleft]{letter}
% \usepackage{hyperref}
\usepackage{fullpage}
\usepackage[margin=1in]{geometry}
\usepackage{multicol}
% \usepackage[hyphenbreaks]{breakurl}
\usepackage[hyphens]{url}
\usepackage{charter}
\signature{\textbf{Student Advisory Board} \\ Kaleo Norman, Chair \\ Bronson Edralin, Vice-Chair \\ Jared Shimabukuro, Secretary \\ Joseph Phillip Felix Jr, Webmaster \\ Christian Josh Bragado Liwanag, Student Fee Representative \\ Kenny Luong, IEEE Student Branch Chair \\ Trevor Alexander, Board Member \\ Colene Pekelo, Board Member}
% \address{1335 Wilder Av. Apt 103 \\ Honolulu, HI 96822 \\ \href{mailto:talex@privatdemail.net}{talex@privatdemail.net} \\ \href{https://www.hitono.info}{https://www.hitono.info}}
\begin{document}

\begin{letter}{Office of the Dean \\ College of Engineering \\ University of Hawaii at Manoa \\ 2540 Dole St., Holmes Hall 240 \\ Honolulu, HI 96822}
\opening{Dear Dean Crouch:}

On October 3rd, an article was published in the Ka Leo (\url{http://www.kaleo.org/news/students-lose-stipends-to-financial-aid/article_d2127484-49bb-11e4-806c-001a4bcf6878.html?mode=print}) regarding a policy that concerns students receiving stipends and financial aid.
Specifically, the article stated that the Office of Financial Aid will be counting stipends received for "voluntary" work, performed by students for the school, as part of their pre-existing financial resources. Furthermore, according to the article, the Office indicated that they would be demanding that a sum equal to the amount of a paid stipend be returned to them in kind, since they view it as a reduction of the student's estimated financial need.

We the Electrical Engineering Student Advisory Board believe this policy is unjust for the following reasons:

\begin{enumerate}
\item The negative consequences of this policy will be \textbf{disproportionately} felt by students in financial need.
\item Students sacrifice their time to work in any paid position, including those paid in stipends. This time is taken away from the same 24 hours available daily for study, sleep, and class attendance, and \textbf{cannot be returned}.
\item The policy exerts a \textbf{chilling effect} on students. Under this unclear and potentially damaging policy, students cannot be sure they will be allowed to keep any money paid to them as part of work for the College of Engineering. This risks depressing student application rates to positions paid through stipends: students will prefer outside employers that allow them to keep their pay, foregoing educational work opportunities that also benefit the College. 
\end{enumerate}

We humbly ask that you issue a clear statement to the student body indicating how the College of Engineering interprets this policy, and what effect it will have on student employment with the College. Regardless of whether or not students will be affected, we deserve to be well-informed, so that we can continue to make the most of the educational opportunities available to us.

Thank you for your time. We look forward to hearing from you on this issue.

\closing{ }


\end{letter}

\end{document}
